Creating the ``r params$package_name`` R package

### 2025-05-30 create-rhello.Rmd
scalar multiple

>>>>

### scalar_mul.predictor_hybrid
Multiplies all components of a `predictor_hybrid` object by a scalar. Functional components are scaled using `times.fd()` from the `fda` package, and scalar predictors are multiplied directly using matrix operations.

```r
scalar_mul.predictor_hybrid(input, scalar)
```

  - `input`: A `predictor_hybrid` object.
  - `scalar`: A numeric value used to scale both scalar and functional components.

- Value:  
Returns a new `predictor_hybrid` object with all components scaled by `scalar`.

- Details:  
  - Functional predictors are scaled using `times.fd(scalar, fd_obj)` for each element.  
  - Scalar predictors (the matrix `Z`) are scaled elementwise using matrix multiplication.

```{r}
#' Multiply a predictor_hybrid object by a scalar
#'
#' Performs scalar multiplication of both scalar and functional components 
#' of a `predictor_hybrid` object. Functional predictors are scaled using 
#' `times.fd()` from the `fda` package.
#'
#' @param input A `predictor_hybrid` object.
#' @param scalar A numeric value to multiply all components by.
#'
#' @return A new `predictor_hybrid` object scaled by `scalar`.
#' @export
scalar_mul.predictor_hybrid <- function(input, scalar) {
  new_functional_list <- lapply(
    input$functional_list,
    function(fd_obj) times.fd(scalar, fd_obj)
  )

  new_Z <- scalar * input$Z

  predictor_hybrid(
    Z = new_Z,
    functional_list = new_functional_list,
    jacobian_list = input$jacobian_list,
    n_basis_list = input$n_basis_list,
    n_sample = input$n_sample,
    n_functional = input$n_functional,
    n_scalar = input$n_scalar
  )
}
```

Here is a test code with two functional predictors:
```{r}
testthat::test_that("scalar_mul.predictor_hybrid works with two functional predictors", {
  suppressPackageStartupMessages(library(fda))

  # Scalar matrix
  Z <- matrix(2, nrow = 3, ncol = 2)

  # Create a shared basis for both functional predictors
  basis <- create.bspline.basis(c(0, 1), 5)

  # Two identical fd objects
  fd1 <- fd(coef = matrix(2, 5, 3), basisobj = basis)
  fd2 <- fd(coef = matrix(2, 5, 3), basisobj = basis)

  # Construct predictor_hybrid object
  obj <- predictor_hybrid(
    Z = Z,
    functional_list = list(fd1, fd2),
    jacobian_list = list(matrix(0), matrix(0)),
    n_basis_list = c(5, 5),
    n_sample = 3,
    n_functional = 2,
    n_scalar = 2
  )

  # Perform scalar multiplication
  scaled <- scalar_mul.predictor_hybrid(obj, 4)

  testthat::expect_s3_class(scaled, "predictor_hybrid")

  # Scalar part should be scaled
  testthat::expect_equal(scaled$Z, Z * 4)

  # Each functional part should be scaled
  expected_coef <- matrix(8, 5, 3)  # 2 * 4
  for (fd_scaled in scaled$functional_list) {
    testthat::expect_equal(
      unname(coef(fd_scaled)),
      unname(expected_coef)
    )
  }
})
```
